Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-01 snapshot_system/result.tex
my local changes

It's easy to see that the time of I/O dominates the backup process, our deduplication
procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
use larger CDS index to cover more of global index, as a result the amount of data to be writen
is reduced and so do the writing time.
Inside the deduplication procedure, the time costs of level-1
is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
because the number of fingerprints to process are just the same.
\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/single_backup_time.pdf, width=3.5in}
  \caption{Time to backup a 40GB VM snapshot under different CDS memory usage settings}
  \label{fig:single_vm_backup}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
  \caption{Throughput per-node with concurrent snapshot backup tasks}
  \label{fig:parallel_backup}
\end{figure}

\subsection{Read Snapshot}

>>>>

It's easy to see that the time of I/O dominates the backup process, our deduplication
procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
use larger CDS index to cover more of global index, as a result the amount of data to be writen
is reduced and so do the writing time.
Inside the deduplication procedure, the time costs of level-1
is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
because the number of fingerprints to process are just the same.

@@

\begin{figure}
    \centering
    \subfigure[Real VM backup performance]
    {
        \includegraphics[width=3in]{figures/parallel_backup_with_read.pdf}
        \label{fig:withread}
    }
    \\
    \subfigure[Deduplication and storage system performance]
    {
        \includegraphics[width=3in]{figures/parallel_backup_no_read.pdf}
        \label{fig:noread}
    }
    \caption{Throughput per-node with concurrent snapshot backup tasks}
    \label{fig:parallel_backup}
\end{figure}

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/srb_vs_vc.pdf, width=3.5in}
  \caption{Time to backup a dirty segment under SRB and VC approach}
  \label{fig:srb_vs_vc}
\end{figure}

% \begin{figure}[htbp]
%   \centering
%   \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
%   \caption{Throughput per-node with concurrent snapshot backup tasks}
%   \label{fig:parallel_backup}
% \end{figure}

% \begin{table}
% \begin{tabular}{ |p{1.5cm}|p{1.8cm}|p{1.2cm}|p{1.4cm}| }
% \hline
%  & Costs & Stateless routing with binning (s) & VM-centric approach (s) \\ \hline
% \multirow{4}{*}{\vbox{I/O related}} & Read data & 0.05 & 0.05 \\ \cline{2-4}
%  & Transfer data  & 0.017 & 0.017 \\ \cline{2-4}
%  & Write data & 0.03 & 0.025 \\ \cline{2-4}
%  & Subtotal & 0.097 & 0.092 \\ \hline
% \multirow{5}{*}{\vbox{Dedupe related}} & Read index/recipe & 0.01 & 0.00045 \\ \cline{2-4}
%  & Write index/recipe & 0.01 & 0.0051 \\ \cline{2-4}
%  & Transfer fingerprints & 0.00058 & 0.00013 \\ \cline{2-4}
%  & CDS lookup & N/A & 0.00034 \\ \cline{2-4}
%  & Subtotal & 0.021 & 0.0064 \\ \hline
% \multicolumn{2}{ |c| }{Total} & 0.12 & 0.098 \\
% \hline
% \end{tabular}
% \caption{Time of backup a segment break down}
% \label{tab:compare}
% \end{table}

\comments{
\subsection{Read Snapshot}
